---
title: "Data Management Tools"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Data Management Tools}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---
```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```
```{r results='hide', message=FALSE}
library(ready4use)
```
Ready4use includes a number of tools for locating, ingesting, inspecting and sharing data for use in open and modular mental health systems models. 

## Specify remote repositories
The `Ready4useRepos` class can be used to specify details of the data repositories used in your data management workflows. 

```{r}
x <- Ready4useRepos(dataverse_nm_1L_chr = "fakes",
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/HJXYKQ",
                    server_1L_chr = "dataverse.harvard.edu")
```

## Ingest data
To ingest all the RDS objects in a specified dataverse dataset, use the `ingest` method. The `ingest` method transforms `x` into an object of class `Ready4useRecord`.

```{r}
x <- ingest(x)
class(x)
```


## Create a data dyad
The `Ready4useDyad` class can be used to pair a dataset with its data dictionary. In the below example, we create a `Ready4useDyad` instance `y` using the data we have just ingested (`x`).

```{r}
y <- Ready4useDyad(ds_tb = x@b_Ready4useIngest@objects_ls$ymh_clinical_tb,
                   dictionary_r3 = x@b_Ready4useIngest@objects_ls$ymh_clinical_dict_r3)
```

## Inspecting data
We can inspect `y` by printing selected information about it to console using the `exhibit` method. If we only wish to see a handful of records, we can pass "head" or "tail" to the `display_1L_chr` argument.

```{r}
 exhibit(y,
         display_1L_chr = "head")
```

By default, exhibit will print the dataset part of the `Ready4useDyad` instance. To see the dictionary, pass "dict" to the `type_1L_chr` argument.

```{r}
exhibit(y,
        type_1L_chr = "dict")
```

## Share data
To share our new object `y`, we first need to specify a target repository that have write persmissions to, using the `Ready4usePointer` class.
```{r}
z <- Ready4usePointer(b_Ready4useRepos = Ready4useRepos(dataverse_nm_1L_chr = "fakes",
                                                        dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/W95KED",
                                                        server_1L_chr = "dataverse.harvard.edu"))
```
We now add details of the targer repository to `y`, transforming it to an instance of the `Ready4useRecord` class.
```{r}
y <- Ready4useRecord(a_Ready4usePointer = z,
                     b_Ready4useIngest = Ready4useIngest(objects_ls = list(y),
                                                         names_chr = c("ymh_clinical_dyad_r4"),
                                                         descriptions_chr = c("An example of a Ready4useDyad - a dataset and data dictionary pair. Note this example uses fake data")))
```

We can now post our new Ready4useDyad object to our dataset (https://doi.org/10.7910/DVN/W95KED). If we wish we can publish the updated dataset in the same step, by using the `publish_dv_1L_lgl` argument.

```{r eval = F}
share(y,
      key_1L_chr = "ENTER THE API KEY FOR YOUR REPO HERE",
      publish_dv_1L_lgl = T)
```


