---
title: "ready4use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ready4use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ready4use)
```
The tools in ready4use are designed to make it easier to find, label and share data for computational health economic models developed with [ready4 framework](https://www.ready4-dev.com).

This development version of the ready4use package has been made available as part of the process of testing and documenting the package. 

A brief overview of the intended use of ready4use tools is provided in the following articles:

- [Ingest Health Economic Model Datasets](V_03.html)
- [Label Health Economic Model Datasets](V_02.html)
- [Share Health Economic Model Datasets](V_01.html)

Additionally, the workflow for finding compatible datasets is described in an [example from youth mental health](https://www.ready4-dev.com/docs/model/datasets/finding-data/search/).

