---
title: "Data Management With Ready4useRepos and Ready4useRecord"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Data Management With Ready4useRepos and Ready4useRecord}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```

Note: **This vignette is illustrated with fake data**. The dataset explored in this example should not be used to inform decision-making.

```{r results='hide', message=FALSE}
library(ready4use)
```
Ready4use includes a number of tools for ingesting and sharing data for open and modular mental health systems models. 

## Specify remote repositories
The `Ready4useRepos` class can be used to specify details of the data repositories used in your data management workflows. Currently, the two types of repository that can be specified in a `Ready4useRepos` class are Dataverse datasets and GitHub releases. `Ready4useRepos` methods for download / upload extend tools from the `dataverse` and `piggyback` packages.

```{r}
X <- Ready4useRepos(dv_nm_1L_chr = "fakes",
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/HJXYKQ",
                    dv_server_1L_chr = "dataverse.harvard.edu",
                    gh_repo_1L_chr = "ready4-dev/ready4",
                    gh_tag_1L_chr = "Documentation_0.0")
```

## Ingest data
To import objects that have been saved as RDS file format in data repositories specified in an `Ready4useRepos` instance, use the `ingest` method. 

The `ingest` method imports all RDS files in the specified repositories unless you request a more targeted approach by supplying the names of desired files to the `fls_to_ingest_chr` argument. By default, the `ingest` method transforms `X` into an object of class `Ready4useRecord`, which pairs the ingested data with metadata describing the ingested data and their provenance. 

```{r}
X <- ingest(X,
            fls_to_ingest_chr = c("ymh_clinical_tb","ymh_clinical_dict_r3"))
```

If metadata are not required, we can simply ingest a list containing the requested objects by supplying the `metadata_1L_lgl = F` argument.

```{r}
## Not run
# objects_ls <- ingest(X,
#                      fls_to_ingest_chr = c("ymh_clinical_tb","ymh_clinical_dict_r3"),
#                      metadata_1L_lgl = F)
```

If we specify just a single object name for ingest, then the `ingest` method returns just that object (instead of a list containing that object).

```{r}
## Not run
# ymh_clinical_tb <- ingest(X,
#                           fls_to_ingest_chr = c("ymh_clinical_tb"),
#                           metadata_1L_lgl = F)
```

## Share data
To illustrate how to share data using `ready4use` classes and methods, we will first need some data to publish. We therefore can create is `Y`, a `Ready4useDyad` [(a data structure explained in another vignette)](V_02.html), using the data we ingested in a previous step (extracted from the `Ready4useRecord` object `X` using calls to the `procureSlot` method.

```{r}
objects_ls <- procureSlot(X,"b_Ready4useIngest") %>% procureSlot("objects_ls")
Y <- Ready4useDyad(ds_tb = objects_ls$ymh_clinical_tb,
                   dictionary_r3 = objects_ls$ymh_clinical_dict_r3) %>%
  renew()
```

We now specify where we plan to publish `Y` in `Z`, a `Ready4useRepos` object. Note, you must have write permissions to the repositories you specify in this step. The values entered in this example (the https://doi.org/10.7910/DVN/W95KED dataset from the [fakes](https://dataverse.harvard.edu/dataverse/fakes)  dataverse will not work for you).

```{r}
Z <- Ready4useRepos(dv_nm_1L_chr = "fakes", # Replace with values for a dataverse & dataset for which
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/W95KED", #  you have write permissions.
                    dv_server_1L_chr = "dataverse.harvard.edu")
```

We can now upload `Y` to our preferred data repository using the `share` method. By default, if more than one data repository was specified in `Z`, then the dataverse repository will be preferred when sharing. We can overwrite this default by passing either "prefer_gh" or "all" values to the `type_1L_chr` argument. The Ready4useDyad object is now available for download at https://doi.org/10.7910/DVN/W95KED.

```{r eval = F}
Z <- share(Z,
           obj_to_share_xx = Y,
           fl_nm_1L_chr = "ymh_clinical_dyad_r4",
           description_1L_chr = "An example of a Ready4useDyad - a dataset (clinical youth mental health, AQoL-6D) and data dictionary pair. Note this example uses fake data.")
```

