---
title: "Share Health Economic Model Datasets"
output: rmarkdown::html_vignette
# output: 
#   rmarkdown::html_vignette:
#     toc: true
#   pdf_document:
#     highlight: null
#     number_sections: yes
vignette: >
  %\VignetteIndexEntry{Share Health Economic Model Datasets}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```

Note: **This vignette is illustrated with fake data**. The dataset explored in this example should not be used to inform decision-making.

```{r results='hide', message=FALSE, warning=FALSE}
library(ready4)
library(ready4use)
```

ready4use includes a number of tools for sharing health economic model data that forms part of the [ready4 framework](https://www.ready4-dev.com). 

## Identify data to be shared
To illustrate how to share data using `ready4use` classes and methods, we will first need some data to publish. In this example, we are going to share `X`, a `Ready4useDyad` [(a data structure explained in another vignette)](https://ready4-dev.github.io/ready4use/V_02.html) that we can create using [data ingested from an online repository](https://ready4-dev.github.io/ready4use/V_03.html).

```{r}
objects_ls <- ingest(Ready4useRepos(dv_nm_1L_chr = "fakes",
                                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/HJXYKQ",
                                    dv_server_1L_chr = "dataverse.harvard.edu",
                                    gh_repo_1L_chr = "ready4-dev/ready4",
                                    gh_tag_1L_chr = "Documentation_0.0"),
                     fls_to_ingest_chr = c("ymh_clinical_tb","ymh_clinical_dict_r3"),
                     metadata_1L_lgl = F)
X <- Ready4useDyad(ds_tb = objects_ls$ymh_clinical_tb,
                   dictionary_r3 = objects_ls$ymh_clinical_dict_r3) %>%
  renew()
```

## Share data
We now specify where we plan to publish `X` in `Y`, a `Ready4useRepos` object ([described in another vignette](https://ready4-dev.github.io/ready4use/V_03.html)). Note, you must have write permissions to the repositories you specify in this step. The values entered in this example (the https://doi.org/10.7910/DVN/W95KED dataset from the [fakes](https://dataverse.harvard.edu/dataverse/fakes)  dataverse will not work for you).

```{r}
Y <- Ready4useRepos(dv_nm_1L_chr = "fakes", # Replace with values for a dataverse & dataset for which
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/W95KED", #  you have write permissions.
                    dv_server_1L_chr = "dataverse.harvard.edu")
```

We can now upload `X` to our preferred data repository using the `share` method. By default, if more than one data repository was specified in `Y`, then the dataverse repository will be preferred when sharing. We can overwrite this default by passing either "prefer_gh" or "all" values to the `type_1L_chr` argument. The Ready4useDyad object is now available for download at https://doi.org/10.7910/DVN/W95KED.

```{r eval = F}
Y <- share(Y,
           obj_to_share_xx = X,
           fl_nm_1L_chr = "ymh_clinical_dyad_r4",
           description_1L_chr = "An example of a Ready4useDyad - a dataset (clinical youth mental health, AQoL-6D) and data dictionary pair. Note this example uses fake data.")
```

