---
title: Ready4useDyad"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Ready4useDyad}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```

Note: **This vignette is illustrated with fake data**. The dataset explored in this example should not be used to inform decision-making.

```{r results='hide', message=FALSE}
library(ready4use)
```

## Create a dataset-dictionary pair
A data dictionary containts useful metadata about a dataset. We can ingest examples of a fake dataset and its data-dictionary [using the method explained in another vignette](V_01.html).

```{r}
objects_ls <- Ready4useRepos(dv_nm_1L_chr = "fakes",
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/HJXYKQ",
                    dv_server_1L_chr = "dataverse.harvard.edu") %>%
  ingest(metadata_1L_lgl = F)
```

Importantly (and a requirement for subsequent steps), the data dictionary we ingest is a `ready4use_dictionary` object.

```{r}
class(objects_ls$eq5d_ds_dict)
```

We can now pair the data dictionary with its dataset in a new object `x`, a `Ready4useDyad`.

```{r}
x <- Ready4useDyad(ds_tb = objects_ls$eq5d_ds_tb,
                   dictionary_r3 = objects_ls$eq5d_ds_dict)
```

## Inspect data
We can inspect `x` by printing selected information about it to console using the `exhibit` method. If we only wish to see the first or last few records, we can pass "head" or "tail" to the `display_1L_chr` argument.

```{r}
 exhibit(x,
         display_1L_chr = "head")
```

The dataset may be more meaningful if variables are labelled using the descriptive information from the data dictionary. This can be accomplished using the `renew` method.

```{r}
x <- renew(x,
           type_1L_chr = "label")
```

```{r}
 exhibit(x,
         display_1L_chr = "head")
```

To remove dataset labels, use the `renew` method with "unlabel" passed to the `type_1L_chr` argument.

```{r}
y <- renew(x,
           type_1L_chr = "unlabel")
```

By default, the `exhibit` method will print the dataset part of the `Ready4useDyad` instance. To inspect the data dictionary, pass "dict" to the `type_1L_chr` argument.

```{r}
exhibit(y,
        display_1L_chr = "head",
        type_1L_chr = "dict")
```

