---
title: "Retrieve Model Datasets"
output: rmarkdown::html_vignette
# output: 
#   rmarkdown::html_vignette:
#     toc: true
#   pdf_document:
#     highlight: null
#     number_sections: yes
vignette: >
  %\VignetteIndexEntry{Retrieve Model Datasets}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```

Note: **This vignette is illustrated with fake data**. The dataset explored in this example should not be used to inform decision-making. 

We recommend also reading the related tutorial available at: https://www.acumen-mh.org/blog/2022/08/28/access_open_data/ 

```{r results='hide', message=FALSE, warning=FALSE}
library(ready4)
library(ready4use)
```

ready4use includes a number of tools for ingesting health economic model data from online repositories and forms part of the [ready4 framework](https://www.ready4-dev.com).

## Specify remote repositories
The `Ready4useRepos` class can be used to specify details of the data repositories used in your data management workflows. Currently, the two types of repository that can be specified in a `Ready4useRepos` class are Dataverse datasets and GitHub releases. `Ready4useRepos` methods for download / upload extend tools from the `dataverse` and `piggyback` packages.

```{r}
X <- Ready4useRepos(dv_nm_1L_chr = "fakes",
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/HJXYKQ",
                    dv_server_1L_chr = "dataverse.harvard.edu",
                    gh_repo_1L_chr = "ready4-dev/ready4",
                    gh_tag_1L_chr = "Documentation_0.0")
```

## Ingest data
To import objects that have been saved as RDS file format in data repositories specified in an `Ready4useRepos` instance, use the `ingest` method. 

The `ingest` method imports all RDS files in the specified repositories unless you request a more targeted approach by supplying the names of desired files to the `fls_to_ingest_chr` argument. By default, the `ingest` method transforms `X` into an object of class `Ready4useRecord`, which pairs the ingested data with metadata describing the ingested data and their provenance. 

```{r}
X <- ingest(X,
            fls_to_ingest_chr = c("ymh_clinical_tb","ymh_clinical_dict_r3"))
```

If metadata are not required, we can simply ingest a list containing the requested objects by supplying the `metadata_1L_lgl = F` argument.

```{r}
## Not run
# objects_ls <- ingest(X,
#                      fls_to_ingest_chr = c("ymh_clinical_tb","ymh_clinical_dict_r3"),
#                      metadata_1L_lgl = F)
```

If we specify just a single object name for ingest, then the `ingest` method returns just that object (instead of a list containing that object).

```{r}
## Not run
# ymh_clinical_tb <- ingest(X,
#                           fls_to_ingest_chr = c("ymh_clinical_tb"),
#                           metadata_1L_lgl = F)
```

